Concurrent Programming with CXL

### 2020-07-02 book/paper.tex
Latest
Improved layout

\begin{figure}
\includegraphics[width=\textwidth]{figures/Up1.png}
\caption{The HTML output of running CXL on Figure~\ref{fig:inc}.
There are four sections.  The top left shows the source code and bytecode
of the program.  The top right shows the steps in an execution.
The middle section shows the values of the variables at a particular step.
The bottom section shows the state of each process.
Each row in the stack trace of a process shows the current program counter,
the method that is being evaluated, and the line of code that is
being evaluated.}
\label{fig:inchtml1}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csbarebones}
\end{code}
\caption{[csbarebones.cxl] A barebones critical section with two processes.}
\label{fig:csbarebones}
\end{figure}

@@

A critical section is often modeled as processes in an infinite loop
entering and exiting the critical section.
Figure~\ref{fig:csbarebones} shows the CVM bytecode.
Here \texttt{@cs} is a \emph{label},
\index{label}%
identifying a location in the CVM bytecode.  The first thing we need to
ensure is that there can never be two processes in the critical section.
This property is called \emph{mutual exclusion}.
\index{mutual exclusion}%
We would like to place an assertion at the \texttt{@cs} label that
specifies that only the current process can be there.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{figures/Up1.png}
\caption{The HTML output of running CXL on Figure~\ref{fig:inc}.
There are three sections.
The top shows the steps to the problematic state.
The bottom left shows the source code and bytecode
of the program.
The bottom right shows the state of each process after the selected step.
Each row in the stack trace of a process shows the current program counter,
the method that is being evaluated, and the line of code that is
being evaluated.}
\label{fig:inchtml1}
\end{figure}

@@

\begin{figure}
\begin{code}
\cxlsource{csbarebones}
\end{code}
\caption{[csbarebones.cxl] A bare bones critical section with two processes.}
\label{fig:csbarebones}
\end{figure}

@@

A critical section is often modeled as processes in an infinite loop
entering and exiting the critical section.
Figure~\ref{fig:csbarebones} shows the CXL code.
Here \texttt{@cs} is a \emph{label},
\index{label}%
identifying a location in the CVM bytecode.  The first thing we need to
ensure is that there can never be two processes in the critical section.
This property is called \emph{mutual exclusion}.
\index{mutual exclusion}%
We would like to place an assertion at the \texttt{@cs} label that
specifies that only the current process can be there.
